### 2025-05-15 download-football-data.qmd
20250514 - NFL standings

```{r}
library("ffanalytics") # to install: install.packages("remotes"); remotes::install_github("FantasyFootballAnalytics/ffanalytics")
library("petersenlab") # to install: install.packages("remotes"); remotes::install_github("DevPsyLab/petersenlab")
library("nflreadr")
library("nflfastR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

@@

nfl_standings_raw <- read_csv("http://www.habitatring.com/standings.csv")
```

@@

```{r}
nfl_standings <- nfl_standings_raw
```

>>>>

```{r}
library("ffanalytics") # to install: install.packages("remotes"); remotes::install_github("FantasyFootballAnalytics/ffanalytics")
library("petersenlab") # to install: install.packages("remotes"); remotes::install_github("DevPsyLab/petersenlab")
library("nflreadr")
library("nflfastR")
library("nflseedR")
library("nfl4th")
library("nflplotR")
library("progressr")
library("lubridate")
library("tidyverse")
```

@@

We can determine NFL standings based on the `nfl_schedules` object using the `nflseedR` [@R-nflseedR] package.

@@

nfl_standings_raw <- nflseedR::nfl_standings(nfl_schedules) #read_csv("http://www.habitatring.com/standings.csv"); archived at: https://perma.cc/5QLN-VK7V
```

@@

```{r}
nfl_standings <- data.frame(nfl_standings_raw)
```

### 2025-05-15 index.qmd
20250512 - OpenHawks grant
20250514 - NFL standings

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nfl4th", "gsisdecoder", "progressr",
  "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", "ggdag",
  "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", "pROC",
  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", "AICcmodavg",
  "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", "viridis",
  "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", "stringi", #"webshot2", 
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin",
  "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", 
  "mgcv", "rms", "car", "performance", "lavaan", "mice", "miceadds","interactions"
)

@@

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nflseedR", "nfl4th", "gsisdecoder", 
  "progressr", "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", 
  "ggdag", "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", 
  "pROC",  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", 
  "AICcmodavg", "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", 
  "viridis", "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", #"webshot2", 
  "stringi", "parallel", "parallelly", "doParallel", "missRanger", "ggridges", 
  "powerjoin", "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", 
  "correlation", "mgcv", "rms", "car", "performance", "lavaan", "mice", 
  "miceadds","interactions", "shiny","PearsonDS","robustbase"
)

@@

This book was supported by an OpenHawks Open Educational Resources grants program from the University of Iowa Libraries.
